\documentclass[11pt, a4paper]{article}

% ---------- Packages ----------
\usepackage[top=1in, bottom=1in, left=1.1in, right=1.1in]{geometry}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black
}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{microtype}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ---------- Section formatting ----------
\titleformat{\section}
  {\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1.2ex plus .2ex minus .2ex}{0.8ex plus .1ex}

% ---------- List spacing ----------
\setlist[itemize]{nosep, leftmargin=1.5em, topsep=2pt}

% ---------- No page number ----------
\pagestyle{empty}

% ======================================
\begin{document}

% ---------- Header ----------
\begin{center}
  {\LARGE \textbf{Soichiro Sugita}} \\[6pt]
  Graduate School of Media and Governance, Keio University \\[3pt]
  \href{mailto:sugita3520@keio.jp}{sugita3520@keio.jp} \quad | \quad
  \href{https://soichiro-sugita.github.io/}{https://soichiro-sugita.github.io/}
\end{center}

\vspace{4pt}

% ---------- Research Interests ----------
\section{Research Interests}

Economics of Education, Labor Economics, Micro-Econometrics

% ---------- Education ----------
\section{Education}

\begin{itemize}
  \item \textbf{Ph.D. Candidate}, Graduate School of Media and Governance, Keio University \hfill April 2022--Present \\
        (On leave: April 2023--September 2024) \\
        Advisor: Makiko Nakamuro

  \item \textbf{M.A.} (Media and Governance), Graduate School of Media and Governance, Keio University \hfill March 2022 \\
        Thesis Supervisor: Makiko Nakamuro

  \item \textbf{B.A.} (Economics), Faculty of Economics, Keio University \hfill March 2020 \\
        Thesis Supervisor: Hiroki Kawai
\end{itemize}

% ---------- Publications ----------
\section{Publications}

\begin{itemize}
  \item Sugita, S. (2026). ``Does Superintendent Turnover Matter? An Empirical Analysis Using Large-Scale Achievement Survey Data.'' \textit{Kokumin Keizai Zasshi (Journal of Economics \& Business Administration)}, 230(2), 1--16.

  \item Sugita, S. (2025). ``The Effect of Class-size Reduction on Students' Well-Being in School.'' \textit{KEIO SFC Journal}, 24(2), 160--170.
\end{itemize}

% ---------- Working Papers ----------
\section{Working Papers}

\begin{itemize}
  \item Sugita, S. (2025). ``The Effect of Class-size Reduction on Students' Well-Being in School.'' \textit{Keio-IES Discussion Paper Series}, DP2025-012.

  \item Sugita, S. (2025). ``Does Superintendent Turnover Matter? An Empirical Analysis Using Large-Scale Achievement Survey Data.'' \textit{Keio-IES Discussion Paper Series}, DP2024-021.

  \item Fujisawa, K., Fukai, T., Sugita, S., and Nakamuro, M. (2022). ``Third-Party Evaluation of Welfare Services and Quality of Childcare: Current Status and Issues.'' \textit{RIETI Discussion Paper Series}, 22-J-042.
\end{itemize}

% ---------- Presentations ----------
\section{Presentations}

\begin{itemize}
  \item ``An Empirical Analysis of Private Middle School Entrance Examinations, Commuting Time, Academic Performance, and Children's QOL Using Japanese Panel Data'' (with Hiroaki Sato, Momoko Oshika, and Makiko Nakamuro). \\
        Japan Economic Association 2026 Spring Meeting (Poster Session), May 2026, Osaka Metropolitan University.

  \item ``The Effect of Class-size Reduction on Students' Well-Being in School.'' \\
        WEAI 100th Annual Conference, June 17, 2025.

  \item ``Does Superintendent Turnover Matter? An Empirical Analysis Using Large-Scale Achievement Survey Data.'' \\
        Japan Public Choice Society 28th Annual Meeting (Poster Session), December 2024, Doshisha University.
\end{itemize}

\end{document}
